\hypertarget{problem-description-and-assignment-description}{%
\section{Problem description and assignment
description}\label{problem-description-and-assignment-description}}

In this chapter will the problem description and task description be
discussed.

\hypertarget{problem-description}{%
\subsection{Problem description}\label{problem-description}}

When different processes operate independently and the sequentiality of
the actions of the processes is important the processes need to be
synchronized. If this sequentiality is not followed programs will
exhibit behavior that is undesirable.\\
For example a payment machine that keeps checking the payment card even
though no product has been selected, this will lead to unneeded
operations.

\hypertarget{assignment-description}{%
\subsection{Assignment description}\label{assignment-description}}

The assignment for this paper is to design and implement a generic
synchronization-server that will synchronize a unknown amount of
processes. These processes will be able to announce their presence to
the synchronization-server, from then on will they be synchronized.\\
The processes and the synchronization-server will be implemented in the
C programming language. The processes will follow from a FSP based
design.

The following elements will be implemented and will be further discussed
in the Requirements,:

\begin{itemize}
\tightlist
\item
  The synchronization-server.
\item
  Multiple processes that will follow from the FSP design.
\item
  Two device-drivers.
\item
  One thread.
\end{itemize}
