\hypertarget{how-will-the-communication-between-processes-take-place-under-minix}{%
\section{How will the communication between processes take place under
Minix}\label{how-will-the-communication-between-processes-take-place-under-minix}}

In this sub-chapter will be explained how a communication between
processes takes place under Minix.

\hypertarget{what-are-messages-and-how-can-they-be-used-to-communicate-between-processes-under-minix}{%
\subsection{What are messages and how can they be used to communicate
between processes under
Minix}\label{what-are-messages-and-how-can-they-be-used-to-communicate-between-processes-under-minix}}

In this sub-question will be explained what messages are and how they
can be send and received under Minix.

\hypertarget{what-are-messages-in-minix}{%
\subsubsection{What are messages in
Minix}\label{what-are-messages-in-minix}}

Minix uses their own message type as payload for sending and receiving
messages. A message are a fixed length of 64 bytes of data, they are
composed of:

\begin{itemize}
\tightlist
\item
  Name ; Explanation
\item
  Endpoint sender ; 4-byte identifier of who sent the message
\item
  Message type ; 4-byte message type identifier
\item
  Payload ; 56 bytes of data
\end{itemize}

To give further explanation about the message type, each message type
has a different structure of its data.

\hypertarget{what-is-an-endpoint-and-how-can-it-be-determined-under-minix}{%
\subsubsection{What is an endpoint and how can it be determined under
Minix}\label{what-is-an-endpoint-and-how-can-it-be-determined-under-minix}}

The following quote from the minix3 wikipedia explains what an endpoint
is and why it is used in Minix:

\begin{quote}
A endpoint identifies a process uniquely among the operating system. It
is composed of the process slot number concatenated with a generation
number.\\
The reason behind this generation number is that a process slot may be
recycled when a process dies, so unrelated processes may sequentially
share the same process slot number, which would cause problems when
delivering messages to a process which happened to share the same
process slot than a unrelated predecessor.
\end{quote}

//TODO add reference

The endpoint of a process can be determined in multiple ways, they are:

\begin{itemize}
\tightlist
\item
  Name ; Explanation ; Input arguments ; Return value
\item
  getpid ; Determines the endpoint of the process calling the function ;
  None ; Endpoint l
\item
  \_pm\_findproc ; Determines the endpoint of the requested process ;
  Process name, Endpoint (endpoint of process will be inserted into this
  parameter) ; Status ;
\end{itemize}

Besides process specific endpoints there are three special endpoints:

\begin{itemize}
\tightlist
\item
  Name ; Explanation ; Usage, there can be more usages than mentioned
  below as these are examples
\item
  Any ; The sender or receiver of the message can be any process ; Can
  be used for broadcasting a message
\item
  None ; The sender or receiver of the message can be no process ; This
  endpoint will not be used and the usage is unknown to the writer at
  the time of writing
\item
  Self ; The sender or receiver of the message is the same process ; Can
  be used to simulate messages that would normally be send from other
  processes
\end{itemize}

\hypertarget{how-can-messages-be-send-and-received-under-minix}{%
\subsubsection{How can messages be send and received under
Minix}\label{how-can-messages-be-send-and-received-under-minix}}

First will be discussed what types of message sending and receiving
Minix supports and then how these can be used.

In Minix there are three basic primitives used to send messages, these
are:

\begin{itemize}
\tightlist
\item
  Name ; Explanation ; Input arguments ; Return value
\item
  Send ; A message is sent, the sender is blocked until the message is
  delivered ; Receiver endpoint, Message ; Status ;
\item
  Receive ; The process is blocked until a message is delivered to them
  ; Sender endpoint, Message, Status ; Status ;
\item
  Sendrec ; A message is sent, the sender is blocked until it receives a
  reply from the receiver ; Receiver endpoint, Message ; Status ;
\end{itemize}

\hypertarget{how-can-memory-be-shared-between-processes-under-minix}{%
\subsection{How can memory be shared between processes under
Minix}\label{how-can-memory-be-shared-between-processes-under-minix}}

In this sub-question will be discusses how data can be communicated
between processes using memory grants under Minix.

\hypertarget{what-is-a-memory-grant-under-minix}{%
\subsubsection{What is a memory grant under
Minix}\label{what-is-a-memory-grant-under-minix}}

Memory grants allow processes to share large amount of data, data that
would be inefficient to send with messages as messages only allow a 56
byte payload.

Every type of memory grant share the same three attributes:

\begin{itemize}
\tightlist
\item
  Permitted access mode may be set to read, write or read-write
\item
  Grants are created by an endpoint for an endpoint
\item
  The memory region is a continuous range with byte granularity
\end{itemize}

The granter is the process that created and owns the grant whereas the
grantee is the process to which the memory grant was granted.

Minix supports three types of memory grants:

\begin{itemize}
\tightlist
\item
  Name ; Explanation
\item
  Direct grants ; A memory region of the granter is accessible by the
  grantee. The data is not transferred from the granter to the grantee,
  the data is only accessible to the grantee and the granter is still
  the owner of the data. This grant is direct because there is no
  middleman
\item
  Indirect grants ; Indirect grants are grants that have been
  transferred by a grantee : the grantee delegates its grant to another
  process. The grantee becomes a granter and then passes a newly created
  memory grant credential to the new grantee. The memory grant thus
  forms a linked list of indirect grants, with a direct grant at the
  start. Indirect grant can themselves be transferred to another grantee
  by creating a new indirect grant.
\item
  Magic grants ; Magic grants are grants that are made by one process
  for memory in another process. The only service that may create magic
  grants, is VFS. VFS uses magic grants to give other services, direct
  access to memory in user application processes.
\end{itemize}

In this paper only the direct grants will be used.

\hypertarget{how-can-memory-grants-be-used-to-share-data-under-minix}{%
\subsubsection{How can memory grants be used to share data under
Minix}\label{how-can-memory-grants-be-used-to-share-data-under-minix}}

As only direct grants will be used in this paper only this type of
memory granting will be further discussed.

In Minix two main function will be used to share data using memory
grants:

\begin{itemize}
\tightlist
\item
  Name ; Explanation ; Input arguments ; Return value
\item
  cpf\_setgrant\_direct ; Grants memory to a specific endpoint and
  returns the grant id ; Endpoint grantee, Memory address of data to
  grant, Memory size in bytes, Access type ; Grant id
\item
  sys\_safecopyfrom ; Copies granted memory from a specific endpoint to
  a memory address ; Endpoint granter, Grant id, Grant offset, Memory
  address to copy data into, Memory size in bytes, Segment ; Status
\end{itemize}

The Access type specifies what kind of access the grantee has over the
memory, either read, write or map.

These two functions combined with sending and receiving messages allow
for sharing data between processes under Minix.
