\hypertarget{research}{%
\chapter{Research}\label{research}}

\hypertarget{how-will-the-communication-between-a-finite-state-machine-and-the-synchronization-server-take-place-under-minix}{%
\section{How will the communication between a finite-state machine and
the synchronization-server take place under
Minix}\label{how-will-the-communication-between-a-finite-state-machine-and-the-synchronization-server-take-place-under-minix}}

In this sub-question will be discussed how the communication between
finite-state machines and synchronization-server will take place under
Minix

\hypertarget{what-is-a-finite-state-machine-status-and-how-will-it-be-communicated-with-the-synchronization-server}{%
\subsection{What is a finite-state machine status and how will it be
communicated with the
synchronization-server}\label{what-is-a-finite-state-machine-status-and-how-will-it-be-communicated-with-the-synchronization-server}}

In this sub-question will be discussed what a finite-state machine
status is and how it will be communicated with the
synchronization-server.

\hypertarget{what-is-a-finite-state-machine-status-and-how-will-it-be-stored}{%
\subsubsection{What is a finite-state machine status and how will it be
stored}\label{what-is-a-finite-state-machine-status-and-how-will-it-be-stored}}

To determine how a finite-state machine will send its status first needs
to be determined what the status of a finite-state machine is.\\
The status of a finite-state machine is all the information needed by
synchronization-server to determine the next action and send the
determined action.

The status will consist of the following finite-state machine
attributes:

\begin{itemize}
\tightlist
\item
  Endpoint
\item
  Sensitivity-list
\item
  Alphabet
\item
  Index, this is the index the finite-state machine its corresponding
  derivative in the list of derivatives held by the
  synchronization-server.
\end{itemize}

These attributes are the only attributes the synchronization-server
needs to determine the next action.

\hypertarget{how-will-a-finite-state-machine-status-be-communicated-with-the-synchronization-server}{%
\subsubsection{How will a finite-state machine status be communicated
with the
synchronization-server}\label{how-will-a-finite-state-machine-status-be-communicated-with-the-synchronization-server}}

The steps of sending a finite-state machine its status are as following:

\begin{itemize}
\tightlist
\item
  Create new finite-state machine status object.
\item
  Copy the attributes mentioned below into the finite-state machine
  status element.
\item
  Create a memory grant that will share the finite-state machine status
  with the synchronization server.
\item
  A new message is created containing the memory grant.
\item
  The message containing the memory grant is send to the
  synchronization-server.
\end{itemize}

When the finite-state machine status message has been send the
synchronization-server will do the following:

\begin{itemize}
\tightlist
\item
  Receive the finite-state machine status.
\item
  Copy the granted memory into a new finite-state machine status object.
\item
  Find the corresponding finite-state machine derivative using the index
  of the finite-state machine status.
\item
  Copy the attributes from the finite-state machine status into the
  finite-state machine derivative.
\end{itemize}

\hypertarget{how-will-the-synchronization-server-communicate-actions-to-the-finite-state-machines}{%
\subsection{How will the synchronization-server communicate actions to
the finite-state
machines}\label{how-will-the-synchronization-server-communicate-actions-to-the-finite-state-machines}}

After the synchronization-server determines the next action the
finite-state machines will execute this action will be send to the
finite-state machines.

The steps of sending the action to the finite-state machines is as
following, this assumes the list of finite-state derivatives that will
execute the action and the action that will be executed is already
determined:

\begin{itemize}
\tightlist
\item
  The list of derivatives that will execute the action is iterated.
\item
  A new message is created containing the to be executed action.
\item
  The message is send using the derivative its endpoint, as this
  endpoint is equal to the finite-state machine its endpoint that will
  execute the action.
\end{itemize}

When a action message has been send the receiving finite-state machine
will do the following:

\begin{itemize}
\tightlist
\item
  Receive the action message.
\item
  Make a transition based upon the received action.
\end{itemize}

After making a finite-state machine makes a transition the finite-state
machine will send its status to the synchronization-server and the
process starts over.
