\hypertarget{research-questions}{%
\chapter{Research Questions}\label{research-questions}}

In this chapter the research questions and the underlying sub-questions
will defined.

\hypertarget{research-question}{%
\section{Research question}\label{research-question}}

This paper has as aim to design and implement a generic synchronization
server. This leads to the following research question:

\begin{itemize}
\tightlist
\item
  How can a synchronization server be build that synchronizes an
  unbeknownst number of threads, where every thread is based on a FSP
  design.
\end{itemize}

\hypertarget{sub-questions}{%
\section{Sub-questions}\label{sub-questions}}

This research question is divided into sub-questions:

\begin{itemize}
\item
  What is the concurrent system architecture that will be used in this
  paper?
\item
  How will the communication between processes take place under Minix?

  \begin{itemize}
  \tightlist
  \item
    What are messages and how can they be used to communicate between
    processes under Minix?

    \begin{itemize}
    \tightlist
    \item
      What are messages in Minix?
    \item
      What is an endpoint and how can it be determined under Minix?
    \item
      How can messages be send and received under Minix?
    \end{itemize}
  \item
    How can memory be shared between processes under Minix?

    \begin{itemize}
    \tightlist
    \item
      What is a memory grant under Minix?
    \item
      How can memory grants be used to share data under Minix?
    \end{itemize}
  \end{itemize}
\item
  How will a finite-state machine be build?

  \begin{itemize}
  \tightlist
  \item
    How will a finite-state machine save its transition-table,
    sensitivity-list and alphabet?

    \begin{itemize}
    \tightlist
    \item
      How will a finite-state machine save its transition-table?
    \item
      How will a finite-state machine save its sensitivity-list?
    \item
      How will a finite-state machine save its alphabet?
    \end{itemize}
  \item
    How will a finite-state machine determine its sensitivity-list and
    alphabet?

    \begin{itemize}
    \tightlist
    \item
      How will a finite-state machine determine its sensitivity-list?
    \item
      How will a finite-state machine determine its alphabet?
    \end{itemize}
  \item
    How will a finite-state machine make transitions?
  \end{itemize}
\item
  How will a synchronization-server be build?

  \begin{itemize}
  \tightlist
  \item
    How will the synchronization-server save the data of the
    finite-state machines?
  \item
    How will the synchronization-server determine the next action for
    the finite-state machines?
  \item
    How will the synchronization-server determine the finite-state
    machines that will execute an action?
  \end{itemize}
\item
  How will the communication between a finite-state machine and the
  synchronization-server take place?

  \begin{itemize}
  \tightlist
  \item
    What is a finite-state machine status and how will it be
    communicated with the synchronization-server?

    \begin{itemize}
    \tightlist
    \item
      What is a finite-state machine status and how will it be stored?
    \item
      How will a finite-state machine status be communicated with the
      synchronization-server?
    \end{itemize}
  \item
    How will the synchronization-server communicate actions to the
    finite-state machines?
  \end{itemize}
\item
  How will the functionality of the device-drivers be implemented?

  \begin{itemize}
  \tightlist
  \item
    How will the functionality of device-driver0 be implemented?
  \item
    How will the functionality of device-driver1 be implemented?
  \end{itemize}
\end{itemize}
